Direction-Free In-Air Signature Verification Using WIFI CSI Signal

### 2019-05-12 190410_Paper_ACPR/paper_v0.tex
paper_acpr: method v1

\begin{document}
%
\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young Woong KWON\inst{1} \and
JooYoung KIM\inst{1} \and
Kar-Ann TOH\inst{1}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Yonsei University \and
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

\section{Related Works}
a. WIFI CSI
b. Siamese Networks

@@

\subsection{Siamese Networks}
- An In-Air Signature Verification System Using Wi-Fi Signals

@@

%system overview
In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
An overview of the proposed scheme is shown in Fig.1.
% main purpose
The main purpose of this system is to receive two csi signals as input, to 
determine if the two signals are the same signature.
Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.
% Figure 1
\begin{figure}
\includegraphics[width=\textwidth]{methods1.eps}
\caption{...} \label{method1}
\end{figure}

\subsection{Data Preprocessing}
% preprocessing
In order to be used as an input to a siamese network, the signal must be pre-processed.

First, the signal have to be converted to non-complex form.
Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref]. so we used absolute of signal only.

% From HC's Papaer
Second, all inputs must be arranged of same size.
Since all signals have different length, the gradient operation with respect to the time instance is adopted to measure the short time energy. 
Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data. 
% HC's end

@@

% Introduce Siamese Net
% From Ref1 start
Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem (Bromley et al., 1993)
Siamese neural networks employ a unique structure to naturally rank similarity between inputs.
It can discriminate between the class-identity of image pairs
The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.[1]
% From Ref1 End

% Functions of Siamese in our system
The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output. 
The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
the network is learned by the back-propagation.

Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.

Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
To classify regardless of the direction of the signal, the model shall be capable of extracting features unrelated to the direction.

% Section: Feature Extraction
\subsubsection{Feature Extraction}
When two processed signals come as the input, they are put to 2 symmetric CNN network.

% CNN: purpose
Purpose of CNN is to extract features from signal.
By sharing their feature map, this CNN networks is trainin to learn characteristics regardless of the direction only.

% how to extract feature using CNN
To perform the feature extraction, we firstly need to have a convolutional neural networks  to serve as the feature extractor
Based on the ConvNet structure [17] the feature extractor of the proposed pretraining model consists of i convolution layers and activation functions followed by i max-pooling layers. Each convolution layer has f∗ filters to be trained, where ∗ = 1, ..., i. In a similar manner, j fully connected layers constitute the classifier of pretraining model where each layer has g•,(•=1,...,j) neurons to be trained.

%Symmetric Architecture
Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures. some may be heavily influenced by the direction in which the signature was entered.
We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.

To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
It was also designed to have the same weight on the symmetrical CNN network as on a symmetrical CNN network.

% tied weights

%Symetric : Share Weights
% To extract the same characteristics from signals in different directions.
% CNN: Feature Extractor
%Automatically extract feature vector from CSI image

@@

\subsubsection{Loss and Backpropagation}
 We impose a regularized cross-entropy objective on our binary classifier.
This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
 We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2. Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
\begin{figure}
\includegraphics[width=\textwidth]{network1.eps}
\caption{...} \label{network1}
\end{figure}

\section{Experiments}
\section{Conclusion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
% Deep Learning Siamese Paper
\bibitem{ref_article1}
Koch, Gregory, Richard Zemel, and Ruslan Salakhutdinov.
 "Siamese neural networks for one-shot image recognition." 
 ICML deep learning workshop. Vol. 2. 2015.
% HC's Conference Paper
 \bibitem{ref_article2}
Moon, Han-Cheol, et al. "An In-Air Signature Verification System Using Wi-Fi Signals." Proceedings of the 2017 4th International Conference on Biomedical and Bioinformatics Engineering. ACM, 2017.
% JS's Conf Paper
\bibitem{ref_article3}
JS's Conf Paper
% Halperin CSI tool paper
\bibitem{ref_article4}
Halperin, Daniel, et al. "Tool release: Gathering 802.11 n traces with channel state information." ACM SIGCOMM Computer Communication Review 41.1 (2011): 53-53.

\end{thebibliography}
\end{document}

>>>>

\begin{document}
%
\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{YoungWoong KWON\inst{1} \and
JooYoung KIM\inst{1} \and
Kar-Ann TOH\inst{1}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Yonsei University \and
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

\section{Related Works}

@@

\subsection{Siamese Networks}
Siamese nets were first introduced in the early 1990s by Bromley and LeCun to solve signature verification as an image matching problem.\cite{koch2015siamese}

@@

\subsection{System Overview}

%system overview

In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
An overview of the proposed system is shown in Fig.1.
% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{methods1.eps}
    \caption{Overview of the proposed system} \label{method1}
\end{figure}

% purpose of the system
This system receives two Wi-Fi CSI signals as input.
The main purpose of the system is to verify if two input signals are of the same signature.

% main purpose1: interpreting CSI 
Our system must have the ability to distinguish signatures by reading Wi-Fi CSI signals.
% verification model
The verification model learns to identify input pairs according to the probability that they belong to the same class or different classes.\cite{koch2015siamese}

% main purpose2: direction free
Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.

Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
To classify regardless of the direction of the signal, we focused on the model shall be capable of extracting features unrelated to the direction.

%% Pre-processing
\subsection{Data Preprocessing}

In order to be used as an input to a siamese network, the signal must be pre-processed.

% used only abs value
First, the signal have to be converted to non-complex form.
Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.

% preprocessing
% From HC's Papaer
Second, all inputs must be arranged of same size.
Since all signals have different length, the gradient operation with respect to the time instance is adopted to measure the short time energy. 
Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
And they are re-sampled uniformly based on Fast Fourier Transform (FFT)  to normalize the length of the data. \cite{moon2017air}
% HC's end

@@

% Functions of Siamese in our system
% Introduce Siamese Net

Siamese neural networks employ a unique structure to naturally rank similarity between inputs. It can discriminate between the class-identity of image pairs.
\cite{koch2015siamese}

Two preprocessed signals enter the Siamese network and the network extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are. The model outputs the probability that the two signals are of the same class. %it is learned by the back-propagation.
This network consists of feature extraction and feature matching part.

% Section: Feature Extraction
\subsubsection{Feature Extraction}

% structure of siamese network
To perform the feature extraction, we firstly need to have a convolutional neural networks to serve as the feature extractor
Based on the ConvNet structure. \cite{lecun1998gradient}

% structure of siamese network
When two processed signals come as the input, they are put to 2 symmetric ConvNet. 
%Symmetric Architecture
Some of the features CNN extracted are related to the shape of the signature, but CNN's features are not just those that helpful to classify signatures. some may be heavily influenced by the direction in which the signature was entered.Structure of the network is shown in Fig.2.
% Figure 2
\begin{figure}
    \includegraphics[width=\textwidth]{network1.eps}
    \caption{Structure of Siamese network} \label{network1}
\end{figure}
% weight tying
We aim to classify the signature in a direction that is not related to the direction in which it was entered. This type of property interferes with the classification of signatures.
To focus on characteristics conducive to classification, The two CNN networks are arranged side by side symmetrically.
It was also designed to have the same weight on the symmetrical CNN network.

% sister networks
This feature extractor is composed of two sister network, which are identical ConvNets with the exact same weights

% CNN: purpose
Purpose of ConvNet in our model is to extract a feature vector from CSI signal. 
%Local Connectivity – image is locally correlated.
Because each CSI signal has a locally related characteristic, the convolution filters apply local connectivity between inputs.
and it helps to extract the feature vector.
and by weight of feature output is shared through all feature map.
%Weight Sharing – overcome enormous weights problem
so it helps to reduce number of weights and can be appliable to CSI signal, which is relatively large size.

% parameters of convnet
this ConvNets are consists of a number of consecutive convolution layers with active functions, and a pooling layer in the end.
the Convolution Layer has n convolution filters in it.

% functions of convnet
Their weights are tied to extract the same characteristics from signals in different directions.
By sharing their feature map, this ConvNet is train to learn characteristics regardless of the direction.

% outputs feature vector
Through a convolution filter, each CSI signal is transformed to a feature vector. this entire process is jointly optimized by backpropagation.

@@

\section{Experiments}

\subsubsection{Loss and Backpropagation}
 We impose a regularized cross-entropy objective on our binary classifier.
This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
 We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2. Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.

\section{Conclusion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%

%\begin{thebibliography}{8}

\bibliographystyle{splncs04}
\bibliography{bib_acpr}

%\end{thebibliography}

\end{document}
